\newcommand{\regexitem}{
    \begin{rg}
    ITEM -> VISIBILITY?

    \hspace{1.8cm}(FUNCTION\_ITEM

    \hspace{1.8cm}| CLASS\_ITEM

    \hspace{1.8cm}| INTERFACE\_ITEM

    \hspace{1.8cm}| IMPORT\_DECLARATION\_ITEM

    \hspace{1.8cm}| TYPE\_ALIAS\_ITEM)

    \hspace{1.8cm}| ENUMERATION\_ITEM
    \end{rg}
}

\newcommand{\regexfunitem}{
    \begin{rg}
    FUNCTION\_ITEM -> \w{fun} IDENTIFIER  GENERIC\_PARAMS?

    \hspace{3.5cm}\w{(}FUNC\_PARAMS?\w{)} FUNC\_RET\_TYPE?
    
    \hspace{3.5cm}(BLOCK\_STATEMENT | \w{;})

    FUNC\_PARAMS -> SELF\_PARAM\w{,}?

    \hspace{3.5cm}| (SELF\_PARAM\w{,})? 

    \hspace{3.5cm}FUNC\_PARAM (\w{,} FUNC\_PARAM)*\w{,}?

    FUNC\_PARAM -> IDENTIFIER\w{:} TYPE

    FUNC\_RET\_TYPE -> \w{->} TYPE

    SELF\_PARAM -> SHORT\_HAND\_SELF | TYPED\_SELF

    SHORT\_HAND\_SELF -> \w{mut}? \w{self}

    TYPED\_SELF -> \w{mut}? \w{self}\w{:} TYPE
    \end{rg}
}

\newcommand{\regexclassitem}{
    \begin{rg}
    CLASS\_ITEM -> \w{class} IDENTIFIER GENERIC\_PARAMS?

    \hspace{3.5cm}EXTENDS\_CLAUSE? IMPLEMENTS\_CLAUSE?

    \hspace{3.5cm}\w{\{} (CLASS\_FIELD)* (CLASS\_METHOD)* \w{\}}

    EXTENDS\_CLAUSE -> \w{ext} TYPE

    IMPLEMENTS\_CLAUSE -> \w{impl} TYPE (\w{,} TYPE)*

    CLASS\_FIELD -> 

    \hspace{3.5cm}VISIBILITY (CONST\_FIELD | VAR\_FIELD)

    CONST\_FIELD -> 

    \hspace{3.5cm}\w{const} IDENTIFIER\w{:} TYPE \w{=} EXPRESSION\w{;}

    VAR\_FIELD -> IDENTIFIER\w{:} TYPE\w{;}

    CLASS\_METHOD -> FUNCTION\_ITEM

    \end{rg}
}

\newcommand{\regexinterfaceitem}{
    \begin{rg}
    INTERFACE\_ITEM -> \w{interface} IDENTIFIER

    \hspace{3.5cm}GENERIC\_PARAMS? EXTENDS\_CLAUSE?

    \hspace{3.5cm}\w{\{} (INTERFACE\_METHOD)* \w{\}}

    INTERFACE\_METHOD -> FUNCTION\_ITEM
    \end{rg}
}

\newcommand{\regeximportitem}{
    \begin{rg}
    IMPORT\_DECLARATION\_ITEM -> \w{import} IMPORT\_TREE\w{;}

    IMPORT\_TREE -> (SIMPLE\_PATH \w{::})? \w{*}

    \hspace{3.8cm}| SIMPLE\_PATH (\w{as} IDENTIFIER | \_)?
    \end{rg}
}
